---
title: "Project 2: stat302.project2 Tutorial"
author: "Xuling Yang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 2: stat302.project2 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
urlcolor: blue
---

\addtolength{\headheight}{-.025\textheight} 
\thispagestyle{fancyplain} 
\rhead{\includegraphics[height=.1\textheight]{logo.png}}
\renewcommand{\headrulewidth}{0pt}

## Introduction

`stat302.project2` is an `R` package that gathers these four main functions written this quarter about Statistical inference and prediction:


\item `my_t.test`, which performs a one sample t-test in R.




In this tutorial, we will explain their usage and test their performance in statistical use.

## Installation

To begin, we need to do some settings, install our package and load useful datasets.

To download the `stat302.project2` package, use the code below.

```{r setup, eval = FALSE}
# install.packages("devtools")
devtools::install_github("xuliny-1834826/stat302.project2")
library(stat302.project2)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Tutorial for `my_t.test`

First, let's do a t-test using this function. We are going to use `lifeExp` data from `my_gapminder`

```{r}
# Hypothesis: H0: mu = 60; Ha: mu != 60

# demonstrate the test using my_t.test
my_t.test(my_gapminder$lifeExp, "two.sided", 60)

# If the p-value we get is less than 0.05, then H0 is rejected, and mu should not be equal to 60; otherwise we fail to reject null.
```

```{r}
# Hypothesis: H0: mu = 60; Ha: mu < 60

# demonstrate the test using my_t.test
my_t.test(my_gapminder$lifeExp, "less", 60)

# If the p-value we get is less than 0.05, then H0 is rejected, and mu should be less than 60; otherwise we fail to reject null.
```

```{r}
# Hypothesis: H0: mu = 60; Ha: mu > 60

# demonstrate the test using my_t.test
my_t.test(my_gapminder$lifeExp, "greater", 60)

# If the p-value we get is less than 0.05, then H0 is rejected, and mu should be greater than 60; otherwise we fail to reject null.
```


## Tutorial for `my_lm`

Second, let's do a t-test using this function. We are going to use `lifeExp` data from `my_gapminder`

