---
title: "Project 2: stat302.project2 Tutorial"
author: "Xuling Yang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 2: stat302.project2 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
urlcolor: blue
---

\addtolength{\headheight}{-.025\textheight} 
\thispagestyle{fancyplain} 
\rhead{\includegraphics[height=.1\textheight]{logo.png}}
\renewcommand{\headrulewidth}{0pt}

## Introduction

`stat302.project2` is an `R` package that gathers these four main functions written this quarter about Statistical inference and prediction:


\item `my_t.test`, which performs a one sample t-test in R.




In this tutorial, we will explain their usage and test their performance in statistical use.

## Installation

To begin, we need to do some settings, install our package and load useful datasets.

To download the `stat302.project2` package, use the code below.

```{r setup, eval = FALSE}
# install.packages("devtools")
devtools::install_github("xuliny-1834826/stat302.project2")
library(stat302.project2)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Tutorial for `my_t.test`

First, let's do a t-test using this function. We are going to use `lifeExp` data from `my_gapminder`

```{r}
# Hypothesis: H0: mu = 60; Ha: mu != 60

# demonstrate the test using my_t.test
my_t.test(my_gapminder$lifeExp, "two.sided", 60)

```


The p-value we get is greater than 0.05. Thus we fail to reject null, which means it is acceptable that mu = 60 in this test, and the real mu is not very far away from 60.


```{r}
# Hypothesis: H0: mu = 60; Ha: mu < 60

# demonstrate the test using my_t.test
my_t.test(my_gapminder$lifeExp, "less", 60)

```

The p-value we get is less than 0.05, then H0 is rejected, which means the real mu is more likely to be less than 60.


```{r}
# Hypothesis: H0: mu = 60; Ha: mu > 60

# demonstrate the test using my_t.test
my_t.test(my_gapminder$lifeExp, "greater", 60)

```
The p-value we get is greater than 0.05. Thus we fail to reject null, which means it is acceptable that mu = 60 in this test, and the real mu is not very far away from 60, and it is not that possible that the mu is greater than 60.

Generally, through all the tests, we can estimate that the real mu is more likely to be less than 60, and is not very far away from 60.

## Tutorial for `my_lm`

Second, let's do a t-test using this function. We are going to use `lifeExp`, `gdpPercap` and `continent` data from `my_gapminder`

```{r}
# demonstrate a regression
my_lm(lifeExp ~ gdpPercap + continent, data = my_gapminder)

# interpret the gdpPercap coefficient

# hypothesis test associated with the gdpPercap coefficient and then interpret

# Use ggplot2 to plot the Actual vs. Fitted values and intepret
```


## Tutorial for `my_knn_cv`

Second, let's do a t-test using this function. We are going to use `species`, `bill_length_mm` and `bill_depth_mm` data from `my_penguins`

